Netwwork meta-analysis of the effect of fungicides for FHB control in Brazil

### 2017-05-02 fhb-meta.Rmd
Update text

---
title: "Meta-analysis of fungicide efficacy for FHB control in Brazil"
output: github_document
---

@@

@@

### Effect size

@@

# difference in yield between treatment and non-treated check
fhb_yield$D <-fhb_yield$yield - fhb_yield$yield_check

# yield and 
fhb_yield$yi2 <- fhb_yield$yield

@@

### Create treatment variables

@@

```{r}
# Number of entries by fungicide and number of sprays
kable(table(fhb_yield$AI, fhb_yield$n_spray2), format="pandoc")

@@

kable(data.frame(table(fhb_trial$year)), format="pandoc")

@@

# Number of trial by location
kable(data.frame(table(fhb_trial$location)), format="pandoc")

@@

# Number of trial by publication
kable(data.frame(table(fhb_trial$publication)), format="pandoc")

# Number of trial by state
kable(data.frame(table(fhb_trial$state)), format="pandoc")

@@

fhb_mv_AI_D <- rma.mv(yi2, vi2,
                      mods = ~ AI_nspray2, 
                      method="ML",random = list(~ AI_nspray2 | trial, ~1 | id),                       struct="UN", 
                      data=fhb_yield, 
                      control = list(optimizer="nlm"))
summary(fhb_mv_AI_D)

@@

### Model 
fhb_mv_AI_cons <- rma.mv(yi2, vi2, 
                         mods = ~ AI_nspray2 * cons_group, 
                         method="ML",
                         random = ~ AI_nspray2 | trial/cons_group, 
                         struct="UN", data=fhb_yield)

>>>>

---
title: "Netwwork meta-analysis of the effect of fungicides for FHB control in Brazil"
output: github_document
---

@@

The data are stored in two csv files, one for FHB index and the other for yield. Each file contains only the selected treatments following a systematic review. See this table which contains the selected trials with summary information for the trial and the reference.

@@

We conducted a two-stage multi-treatment or network meta-analysis for the simultaneous analysis of all treatments of interest and which co-occur in the same trial. This approach allows direct comparisons of treatments with each other, and takes into account all the correlations (see Madden et al. 2016 for more details).

The most common form of effect size used in traditional meta-analysis are based on the contrasts of the treatment of interest with a common reference (e.g. control treatment), such as mean difference, response ratio, etc. This is known as the conditional modeling approach, also named contrast-based meta-analysis. An alternative and simpler approach, which is commonly used in plant pathology, is to fit a two-way linear mixed model directly to the treatment means. This is know as the uncondional modeling approach or arm-based meta-analysis.

Here, we used the latter approach fitted directly to the log of the means (for both FHB index and yield) for further obtaining the relative effect (control efficacy and yield response). For yield, we fitted the model directly to the mean yield of treatments to further estimate the yield response, or the difference (D) from using the fungicides. The D was calculated for each treatment within a study for plotting purposes, but the meta-analyitic estimate of D was obtained from the difference of the estimates by mixed model fitted directly to the treatment means.

### Effect size calculations

@@

# difference (D) in yield between treatment and non-treated check
fhb_yield$D <-fhb_yield$yield - fhb_yield$yield_check

@@

### Prepare the treatment variables

@@

```{r}
# Number of entries by fungicide and number of sprays
table(fhb_yield$AI, fhb_yield$n_spray2)

@@

data.frame(table(fhb_trial$year))

@@

# Number of trial by location
data.frame(table(fhb_trial$location))

@@

# Number of trial by publication
data.frame(table(fhb_trial$publication))

# Number of trial by state
data.frame(table(fhb_trial$state))

@@

fhb_mv_AI_D <- rma.mv(yield, vi2,
                      mods = ~ AI_nspray2, 
                      method="ML",random = list(~ AI_nspray2 | trial, ~1 | id),                       struct="UN", 
                      data=fhb_yield, 
                      control = list(optimizer="nlm"))
summary(fhb_mv_AI_D)

@@

### Model 
fhb_mv_AI_cons <- rma.mv(yield, vi2, 
                         mods = ~ AI_nspray2 * cons_group, 
                         method="ML",
                         random = ~ AI_nspray2 | trial/cons_group, 
                         struct="UN", data=fhb_yield)
